\myTitle

### 2023-11-16 body-text-of-paper.tex
updated some results, added some figures to folder

Genetic samples were collected from 160 invasive wild pigs across a SPATIAL EXTENT in 
southeastern Missouri that were lethally removed through population control efforts conducted 
as a component of the Missouri Feral Hog Elimination Partnership
by US Department of Agriculture – Animal Plant Health Inspection Services – Wildlife Services, Missouri Department of Conservation, 
and other cooperative state agencies CHECK.
DNA was extracted from hair or tissue (collected from animals at the time of euthanasia) with 
commercially available magnetic bead recovery kits (MagMax DNA, Thermo Fisher Scientific).
Genotyping was performed with GeneSeek’s Genomic Profiler for Porcine HD which provides 
62,128 biallelic SNP loci that are mapped across the 18 autosomal chromosomes.
We implemented standard genotype quality control metrics, specifically, we pruned genotypes with 
call rates <95\% and minor allele frequencies <5\%.
We implemented linkage disequilibrium (LD) pruning using a window size of 50 loci and step size 
of 5 loci to remove markers above a linkage threshold of $R^2 > 0.5$.

@@

Using the 120 reference individuals, we sought to classify the admixture patterns of the 40 empirical samples 
from the contact regions using simulated pedigrees from \gscramble{}. To address this objective we simulated 
pedigrees to represent the likely classes of admixed individuals that would be present in the samples 
from the contact regions of the 3 reference populations. The types of admixed individuals we considered were 
all two-population combinations of $F_1$, $F_2$, $B_1$ and $B_2$. We also 
simulated individuals from each of the founder populations. The first step of this workflow involved 
simulating admixed individuals for 2 founder populations using one of the preset \gscramble{} 
GSPs provided by the function {\footnotesize\tt create\_GSP()} for producing each of the types of admixed 
individuals. While we could have simulated all 4 types of admixed individuals from a single GSP (Figure~\ref{fig:gsp2}), 
different numbers of simulated individuals are produced for each hybrid class. Therefore, for the sake of the 
computational efficiency from simulating the exact number of desired individuals, we chose to simulate from 
a single GSP for each of the hybrid classes by setting the corresponding hybrid parameter in {\footnotesize\tt create\_GSP()} to {\footnotesize\tt TRUE}. We used the default settings of the {\footnotesize\tt plink\_map2rec\_rates()} to specify the recombination rates. The 120 simulated genotypes were written to PLINK .ped and .map files using {\footnotesize\tt gscramble2plink()}. We used PLINK version 1.9 \citep{purcell2007plink} to convert the genotypes to binary files and used these as input into ADMIXTURE for which we specified $K=3$ to produce ancestry values. We iteratively 
performed this workflow to produce 1,000 simulated genotypes and ancestry values for each of the 
4 hybrid classes, as well as founder individuals, for each of the population combinations, for a total of 
21,000 simulated individuals.

@@

SNP filtering resulted in 14,233 loci that were used for subsequent analysis. Using the 160 empirical samples, ADMIXTURE results supported the identification of 3 genetic clusters (SUPPLEMENTAL FIGURE CROSS VALIDATION?). Admixture *q* values clearly grouped individuals from each of the core populations into 3 clusters while the 40 individuals from the contact regions were highly admixed (SUPPLEMENTAL FIGURE ADMIXTURE). The
$F_{ST}$ divergence from ADMIXTURE was: $F_{ST} = 0.243$ for Pop1-Pop2, $F_{ST} = 0.145$ for Pop1-Pop14 and $F_{ST} = 0.133$ for Pop2-Pop14.

>>>>

Genetic samples were collected from 160 invasive wild pigs in 
southeastern Missouri that were lethally removed through population control efforts conducted 
as a component of the Missouri Feral Hog Elimination Partnership
by US Department of Agriculture – Animal Plant Health Inspection Services – Wildlife Services, Missouri Department of Conservation, 
and other cooperative state agencies CHECK.
DNA was extracted from hair or tissue (collected from animals at the time of euthanasia) with 
commercially available magnetic bead recovery kits (MagMax DNA, Thermo Fisher Scientific).
Genotyping was performed with GeneSeek’s Genomic Profiler for Porcine HD which provides 
62,128 biallelic SNP loci that are mapped across the 18 autosomal chromosomes.
We implemented standard genotype quality control metrics, specifically, we pruned genotypes with 
call rates $<95\%$ and minor allele frequencies $<5\%$.
We implemented linkage disequilibrium (LD) pruning using a window size of 50 loci and step size 
of 5 loci to remove markers above a linkage threshold of $R^2 > 0.5$.

@@

Using the 120 reference individuals, we sought to classify the admixture patterns of the 40 empirical samples 
from the contact regions using simulated pedigrees from \gscramble{}. To address this objective we simulated 
pedigrees to represent the likely classes of admixed individuals that would be present in the samples 
from the contact regions of the 3 reference populations. The types of admixed individuals we considered were 
all two-population combinations of $F_1$, $F_2$, $BC_1$ and $BC_2$. We also 
simulated individuals from each of the founder populations. The first step of this workflow involved 
simulating admixed individuals for 2 founder populations using one of the preset \gscramble{} 
GSPs provided by the function {\footnotesize\tt create\_GSP()} for producing each of the types of admixed 
individuals. While we could have simulated all 4 types of admixed individuals from a single GSP (Figure~\ref{fig:gsp2}), 
different numbers of simulated individuals are produced for each hybrid class. Therefore, for the sake of the 
computational efficiency from simulating the exact number of desired individuals, we chose to simulate from 
a single GSP for each of the hybrid classes by setting the corresponding hybrid parameter in {\footnotesize\tt create\_GSP()} to {\footnotesize\tt TRUE}. We used the default settings of the {\footnotesize\tt plink\_map2rec\_rates()} to specify the recombination rates. The 120 simulated genotypes were written to PLINK .ped and .map files using {\footnotesize\tt gscramble2plink()}. We used PLINK version 1.9 \citep{purcell2007plink} to convert the genotypes to binary files and used these as input into ADMIXTURE for which we specified $K=3$ to produce ancestry values. We iteratively 
performed this workflow to produce 1,000 simulated genotypes and ancestry values for each of the 
4 hybrid classes, as well as founder individuals, for each of the population combinations, for a total of 
21,000 simulated individuals.

@@

SNP filtering resulted in 14,233 loci that were used for subsequent analysis. 
Using the 160 empirical samples, ADMIXTURE results supported the identification of 
3 genetic clusters (SUPPLEMENTAL FIGURE). Admixture $q$ values clearly grouped individuals 
from each of the core populations into 3 clusters while the 40 individuals from the contact regions were 
highly admixed (SUPPLEMENTAL FIGURE). The
$F_{ST}$ divergence from ADMIXTURE was: 
$F_{ST} = 0.24$ for Pop1-Pop2, 
$F_{ST} = 0.14$ for Pop1-Pop14 and 
$F_{ST} = 0.13$ for Pop2-Pop14.

The simulated hybrid classes produce 
the expected range of admixture with $F_1$ and $F_2$ individuals having mean $q=0.5$, with $F_2$ individuals having 
more variation. Backcrossed individuals have higher ancestry associated with the backcrossed population with $q$ 
approximately $0.75$ ($BC_1$) and $0.875$ ($BC_2$) (Figure~\ref{fig:pig-sim-qs}).

%%%
\begin{figure*}
\newcommand{\pigsimsqscap}{\footnotesize ADMIXTURE estimates of $q$ for $K=3$ of the simulated hybrid classes 
($F_1$, $F_2$, $BC_1$ and $BC_2$) from all two-population combinations of the invasive wild pig genotypes. 
Rows and columns provide the population combinations of the hybrids and for backcrossed hybrids the rows 
specify the backcrossed population. Plots where the rows and columns specify the same population depict the 
$q$ values for simulated non-hybrid (or "Core") individuals from the population.}
\includegraphics[width=0.96\textwidth]{figures/simulated-pigs-Q-facet.pdf}
\caption[\pigsimsqscap]{\pigsimsqscap}
\label{fig:pig-sim-qs}
\end{figure*}
%%%
